GMSE: an R package for generalised management strategy evaluation

### 2018-04-30 notebook/ms/SI3.Rmd
Major add of vignettes and relevant data

```{r, echo = FALSE, eval = TRUE}
load("data/SI3-cull_sim.rda"); # Avoids long compiling time
sim_1 <- sim;
```

@@

```{r, echo = FALSE, eval = TRUE}
load("data/SI3-scare_sim.rda"); # Avoids long compiling time
sim_2 <- sim;
```

>>>>

```{r, echo = FALSE, eval = TRUE}
load("../data/SI3-cull_sim.rda"); # Avoids long compiling time
sim_1 <- sim;
```

@@

```{r, echo = FALSE, eval = TRUE}
load("../data/SI3-scare_sim.rda"); # Avoids long compiling time
sim_2 <- sim;
```

### 2018-04-30 notebook/ms/SI5.Rmd
Major add of vignettes and relevant data

```{r}
temp_dir <- tempdir()
download.file("http://flr-project.org/doc/src/loading_data.zip", file.path(dir, "loading_data.zip"))
unzip(file.path(temp_dir, "loading_data.zip"), exdir = temp_dir);
```

@@

```{r}
fish_data <- read.csv(file.path(temp_dir, "catch_numbers.csv"), row = 1);
fish_data <- as.matrix(fish_data);
print(fish_data[,1:8]);
```

>>>>

```{r}
#temp_dir <- tempdir()
#download.file("http://flr-project.org/doc/src/loading_data.zip", file.path(dir, "loading_data.zip"))
#unzip(file.path(temp_dir, "loading_data.zip"), exdir = temp_dir);
```

@@

```{r}
#fish_data <- read.csv(file.path(temp_dir, "catch_numbers.csv"), row = 1);
#fish_data <- as.matrix(fish_data);
#print(fish_data[,1:8]);
```

### 2018-04-30 notebook/ms/ms.Rmd
Minor edit
Major add of vignettes and relevant data

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy Rakotonarivo&#xb9;,
  Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk,
  Biological and Environmental Sciences 3A149 University of Stirling Stirling, FK9
  4LA, UK'
output:
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{GMSE, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
linestretch: 2
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
biblio-style: apalike
---

@@

The R package 'GMSE' is a flexible modelling tool to simulate all key aspects of natural resource management. GMSE offers a range of parameters to simulate resource dynamics and management policy options, and includes genetic algorithms to dynamically model stakeholder (manager and user) decision-making. Genetic algorithms find adaptive solutions to any simulated conditions given stakeholder-specific goals, allowing GMSE to model scenarios of conservation conflict.

>>>>

---
title: 'GMSE: an R package for generalised management strategy evaluation'
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy Rakotonarivo&#xb9;,
  Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk,
  Biological and Environmental Sciences 3A149 University of Stirling Stirling, FK9
  4LA, UK'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[R]{GMSE, AN R PACKAGE}
- \usepackage{lineno}
- \linenumbers
linestretch: 2
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
biblio-style: apalike
---

@@

The R package 'GMSE' is a flexible modelling tool to simulate key aspects of natural resource management. GMSE offers a range of parameters to simulate resource dynamics and management policy options, and includes genetic algorithms to dynamically model stakeholder (manager and user) decision-making. Genetic algorithms find adaptive solutions to any simulated conditions given stakeholder-specific goals, allowing GMSE to model scenarios of conservation conflict.
